\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-03-12 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
section 1 updated

\medskip
The objective of this study is to investigate and describe the behaviour of viscous fingering. The CVFE method  will use a conservative computational multi-fluid porous media formulation able to exploit the mesh adaptivity on fully-unstructured tetrahedral grids. Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) the overlapping control volume finite element method formulation.

\medskip
In the sections following the introduction, numerical formulation and a summary of the main governing equations for multiphase compositional flows will follow. The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions. The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.

>>>>

\medskip
The objective of this study is to investigate and describe the behaviour of viscous fingering through a novel CVFE formulation that exploits adaptive mesh of fully triangle and tetrahedron grids. Also two key characteristics that describe the research concept above are: (a) the hybrid element pair $P_{n}DGP_{m}$ which provides discontinuous and piecewise representation for velocity and continuous and piecewise representation of pressure at FE space and (b) a dual representation of pressure and velocity fields in teh FE and CV spaces.

\medskip
In the next sections the numerical formulation and a summary of the main governing equations for multiphase compositional flows will discussed. The remainder of the paper will include a description of the viscous fingering along with the finite element method technique, a discussion of the test-cases and the simulation results and the key conclusions. The analysis will consider ($1$)permeability heterogeities, ($2$)capturing the development of the interface and the evolution of fingers, ($3$)test-case comparison, but for now will neglect any gravitational effects.
